\subsection{Checklist}
% a checklist that describes things that have been done and things that are yet to be done
\begin{itemize}
    \item[\checkmark] \textbf{Literature Review and Method Proposal (Completed).}
    \begin{itemize}
        \item Conducted a comprehensive literature review on SRT and CoT faithfulness.
        \item Finalized the research formulation: measuring reasoning--answer faithfulness using a two-model framework (Model~A = Qwen, Model~B = LLaMA).
        \item Defined evaluation metrics (OMR, MWC, MWW, Flip Rates) and designed the inference–evaluation pipeline schema.
    \end{itemize}

    \item[\checkmark] \textbf{Dataset and Infrastructure Setup (In Progress).}
    \begin{itemize}
        \item Selected the DAPO-Math-17k dataset as the benchmark for multi-step reasoning.
        \item Initialized repository structure and development environment (PyTorch, vLLM, Hydra, W\&B).
        \item Implementing standardized data loader and preprocessing utilities for batched inference and logging.
    \end{itemize}

    \item[\phantom{\checkmark}] \textbf{Inference and Evaluation Pipeline (Next).}
    \begin{itemize}
        \item Build Model~A inference using vLLM with automatic CoT extraction and efficient batching.
        \item Develop Model~B evaluation module that takes masked CoT input and reconstructs Model~A’s answer via prompt templates.
        \item Integrate metric computation and generate baseline quantitative results (OMR, MWC, MWW).
    \end{itemize}

    \item[\phantom{\checkmark}] \textbf{Faithfulness Intervention and Qualitative Study (Planned).}
    \begin{itemize}
        \item Implement perturbation-based interventions: CoT truncation ($k=\{1,2\}$ steps) and error injection (arithmetic/logical flips).
        \item Compute Truncation and Mistake Flip Rates to assess causal dependence between CoT and final answers.
        \item Conduct manual annotation of 50 stratified samples to categorize decorative, causal, and underspecified reasoning patterns.
    \end{itemize}

    \item[\phantom{\checkmark}] \textbf{Evaluation Summary and Final Report (Planned).}
    \begin{itemize}
        \item Aggregate quantitative and qualitative findings and prepare visualization materials.
        \item Finalize figures, tables, and analyses for the written report and presentation.
        \item Verify reproducibility and submit the complete deliverables by the final deadline.
    \end{itemize}
\end{itemize}


\subsection{Tasks division}
% who in your team is working on each task
\begin{itemize}
    \item \textbf{Zhiyun Zhang}: Build a MATH dataset processing and inference pipeline for Model~A (Qwen) and Model~B (LLaMA), and analyze Model~A’s generated answers.
    \item \textbf{Tony Li}: Establish baselines by providing Model~B with only the prompt and the CoT to produce the final answer, and evaluate its performance.
    \item \textbf{Riyaz Ahuja}: Implement CoT truncation and perturbation mechanisms and analyze their effect on answer consistency.
    \item \textbf{George Wu}: Conduct manual inspection of representative samples to characterize reasoning faithfulness.
\end{itemize}


\subsection{Timeline}
% a timeline with specific milestones
\begin{itemize}
    \item \textbf{Phase 1} (by Nov 7): \textbf{ Literature Review and Method Proposal.}\\
    Conducted a comprehensive review of prior works on SRT and CoT faithfulness.  
    Finalized problem formulation, evaluation framework, and dataset specification.

    \item \textbf{Phase 2} (by Nov 17): \textbf{ Pipeline and Baseline Implementation.}\\
    Develop inference and evaluation pipeline for Qwen and LLaMA using PyTorch/vLLM.  
    Standardize data format and enable baseline evaluation where Model~B reconstructs Model~A’s answers from CoTs.

    \item \textbf{Phase 3} (by Nov 27): \textbf{ Faithfulness Intervention Study on $\text{CoT}_A$.}\\
    Run experiments with perturbation-based interventions to test causal dependence between reasoning and final outputs.  
    Compute OMR, MWC, MWW, and flip rates; perform qualitative inspection of reasoning behaviors.

    \item \textbf{Phase 4} (by Dec 5): \textbf{ Evaluation and Final Report Preparation.}\\
    Aggregate findings, visualize results, and finalize report and presentation materials.  
    Verify reproducibility and submit the complete deliverables.
\end{itemize}


\subsection{Current Progress}
% one or two paragraphs describing the current progress. We also ask that you share the github link to your repository in this section.

Our team has completed the literature review and finalized the methodological design for evaluating chain-of-thought faithfulness.  
The DAPO-Math-17k dataset has been selected, and the development environment is configured.  
We are currently implementing the standardized data loader and schema integration into the inference pipeline.  
The next milestone is to complete the Model~A/Model~B inference--evaluation loop and begin baseline metric computation.  
Faithfulness intervention experiments and qualitative analysis will follow once the baseline pipeline is stable.  

\noindent
Project repository: \textbf{\url{https://github.com/daisy-zzy/10701-project}}
